---
title: ''
output: 
    #pdf_document: 
    bookdown::word_document2: 
      reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
  #officedown::rdocx_document
bibliography: references.bib
csl: methods-in-ecology-and-evolution.csl



---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\raggedright

**Title:** Technical workflow for near real-time reporting of forest census results


**Authors (tentative / incomplete list, not in order):** 


David Mitre

Valentine Herrmann^1^ ( Orcid ID : 0000-0002-4519-481X)

Jess Shue

Krystal Bagnaschi

Rachel Hoffman

Iris Kennedy

Erin MacMonigle

Caroline Troy

Luca Morreale

Albert Kim?

Lukas Magee

Daniel Zuleta

Stuart Davies?

(others)

William McShea

Kristina J. Anderson-Teixeira^1,2^* ( Orcid ID : 0000-0001-8461-9713)






**Author Affiliations:**

1. Conservation Ecology Center; Smithsonian's National Zoo & Conservation Biology Institute; Front Royal, Virginia 22630, USA

2. Forest Global Earth Observatory, Smithsonian Tropical Research Institute, Apartado Postal 0843-03092, Panama City, Panama


*corresponding author: teixeirak@si.edu; +1 540 635 6546

**Running head:** <!-- ≤45 characters-->



<!--JOURNAL

Target journal: Methods in Ecology & Evolution
Instructions for authors: https://besjournals.onlinelibrary.wiley.com/hub/journal/2041210X/author-guidelines
article type: research article or practical tools
word count: (no more than 7000-8000 words for Standard Articles, 3000-4000 words for Applications and Practical Tools)

Research article:  should have a maximum of 7000-8000 words (including tables/figure captions and references list) and describe new methods and how they may be used. We place emphasis on methods that are applicable as broadly as possible. Papers describing methods that apply to one species or system are unlikely to meet these criteria, unless authors are able to show that their methods can be generalised. Structure: see Manuscript specifications below.

Practical Tools: Short (no more than 3000-4000 words total) descriptions of new field techniques, equipment or lab protocols. Articles need to clearly demonstrate how tools designed for specific systems or problems can be adapted for more general use. Online supporting information may include specific instructions, especially for building equipment. Practical Tools papers are made free to access for two months after being assigned to an issue in order to encourage uptake of the methodologies they describe. See examples here.I don't think GCB has an official limit on display items (a recently accepted article has 10 figures and 4 tables). -->


```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
# DISPLAY ITEMS
## I do not see any guidance as to the number of display items allowed in MEE.

#Tables
## example = 1 

#Figures
schematic = 1

```

\newpage

# Abstract  {-#Abstract} 

<!--The abstract must not exceed 350 words and should list the main results and conclusions, using FOUR simple, factual, numbered statements:

1: set the context for and purpose of the work;

2: indicate the approach and methods;

3: outline the main results;

4: identify the conclusions and the wider implications.-->


**Keywords**:  <!--A list in alphabetical order not exceeding eight words or short phrases. The most important key-words should appear in the title and the abstract as well as the key-word list. -->

\newpage

# Introduction  
<!-- This should state the reason for doing the work, the nature of the hypothesis or hypotheses under consideration, and should outline the essential background. -->

*Par. 1: Forests are important for climate regulation and support of biodiversity (UN goals). Therefore we need quality, up-to-date data on forest C and biodiversity.*

*Par. 2: While remote sensing is vital to mapping forest biomass and diversity globally, ground-based censuses are essential for calibrating/ interpreting satellite data. In short, ground-based censuses are vital to quantifying forest C, diversity, and trends therein.*

*Par. 3: Yet, collection of accurate census data is not trivial. (challenges include developing a good, efficient system for recording data and time lags in checking data)*

*Par 4: To address these challenges, we have developed a workflow for data collection, quality control, and automated production and publication of results. THis is developed at ForestGEO sites, but applicable to any forest census. *


**Figure: workflow diagram**

# Materials and Methods 
<!--Include sufficient details for the work to be repeated. Where specific equipment and materials are named, the manufacturer’s details (name, city and country) should be given so that readers can trace specifications by contacting the manufacturer. Where commercially available software has been used, details of the supplier should be given in brackets or the reference given in full in the reference list. Do not describe or refer to commonplace statistical tests in this section but allude to them briefly in Results.-->


## Step 1: Production of Digital Data Records from Field Census

Data were collected via a variety of mechanisms, ultimately leading to digital data files.
Here, we applied three different methods for censuses at ForestGEO plots.

### ArcGIS App
Examples: BCI, SCBI 

**Figure: screenshots of app, including examples from both BCI and SCBI**

### Fast Field Forms App
Examples (potential): Wabikon, Tyson, and Lilly Dickey (2022)

**Figure?: screenshots of app**

### Paper Records 
Example: Amacayacu

At Amacayacu, paper records were collected in the [YEAR] census. 
Data were digitized (entered into spreadsheets) every weekend.
Here, we analyzed digital records as collected in the field (no corrections applied).

## Step 2: Automated Data Processing via GitHub Actions
### Data QA/QC
### Biological Results
Generate maps & .csv files for each of the following (by quadrat, as soon as each quadrat is completed and found to be error-free):

- n stems
- n gained (recruitment)
- n lost (mortality)
- ∆ n stems
- biomass
- woody productivity
- woody mortality
- ∆ biomass 
- species richness
- n species gained
- n species lost
- ∆ species richness

### Results Dashboard
*(Luca will tackle this. We'll use GitHub pages.)*


### Step 3: Finalizing Data with Species ID of Recruits
Tropical sites typically have a large lag between data collection and finalization because all new recruits must be identified to species. 
Given high species diversity, it is not possible for even expert botanists to identify all species in teh field; rather, specimens must be collected and identified later with reference to botanical collections.
This process can take years, meaning that census data are often not finalized until years after the census has been completed.
While this process must be completed in order to quantify species richness, stem abundance can be calculated, and biomass estimated, before this process is complete. 


# Results 
<!--State the results and draw attention in the text to important details shown in tables and figures.-->
## Error Rates and Detection

## Biological Results

# Discussion 
<!--This should point out the significance of the results in relation to the reasons for doing the work, and place them in the context of other work.-->

# Conclusions (optional)

# Acknowledgements {-#Acknowledgements}

- Funding: ForestGEO


# Conflict of Interest statement {-#Conflict}
The authors declare no conflict of interest.

# Authors' contributions {-#Authors}
*[Name of author 1] and [Name of author 2] conceived the ideas and designed methodology; [Name of author 1] and [Name of author 3] collected the data; [Name of author 2] and [Name of author 4] analysed the data; [Name of author 1] and [Name of author 4] led the writing of the manuscript. All authors contributed critically to the drafts and gave final approval for publication.*

# Data availability {-#Data}


\newpage
# References {-#References}




